\bf\mftitle

### 2011-01-25 doc/jInfer/architecture/architecture.tex
UML like adaptation, not done
Changed type of arrows to empty for uml-like diagrams
Documentation: Architecture: adding required metadata reference.

The first stands for bare node in XML document tree, it has its name and context withing the tree (path from root).
The latter two extends \code{NamedNode} interface.
\code{StructuralNode} is for nodes, which form structure of XML document tree: elements and text nodes.
\code{ContentNode} is for nodes, that have content in XML documents: text nodes and attributes.
We have three classes: \code{Element} for elements, \code{SimpleData} for text nodes, \code{Attribute} for attributes (see package \code{cz.cuni.mff.ksi.jinfer.base.objects.nodes}).
In theory, the classes and interfaces would be layed out as on fig. \ref{interfaces_nodes}
\begin{figure}
\centering\includegraphics[scale=\myscale]{interfaces_nodes}
\caption{How should interfaces and classes for XML representation look like in theory} \label{interfaces_nodes}
\end{figure}
\begin{figure}
\centering\includegraphics[scale=\myscale]{nodes}
\caption{How are interfaces and classes for XML representation arranged in practice} \label{nodes}
\end{figure}
\begin{figure}
\centering\includegraphics[scale=\myscale]{nodes_full}
\caption{XML representing interfaces and classes in detail} \label{nodes_full}
\end{figure}

@@

At the present, jInfer modules use the following metadata, all defined in \code{IGGUtils} class:
\begin{itemize}
	\item \code{from.xml}, filled in by BasicIGG module: means that this rule was created (originates from) from a XML document.
	\item \code{from.schema}, filled in by BasicIGG and XSDImport modules: means that this rule was created (originates from) from a schema.
	\item \code{from.query}, filled in by BasicIGG and XSDImport modules: means that this rule was created from a query.
	\item \code{is.sentinel}, filled in by  BasicIGG and XSDImport module: when importing XML document, one can build whole tree in memory (as in fig. \ref{xml_example}) and then construct list of rules from it (thus saving memory). With schema import however, one not only doesn't know right side of rule in advance (solved by stack in XML import), but right side can be defined anywhere in source file. To save complicated loading of whole schema, searching and pairing elements thorough rules, nodes on right side of rule are created empty - holding only name of node. Fact, that this node has no more information than it's name and position on right side of rule is denominated by labeling the node as sentinel.
\end{itemize}
All of these metadata are of set/not set character (using \code{Boolean.TRUE} as value, but their presence effectively mean true).

>>>>

The first stands for bare node in XML document tree, it has its name and context withing the tree (path from root).
The latter two extends \code{NamedNode} interface.
\code{StructuralNode} is for nodes, which form structure of XML document tree: elements and text nodes.
\code{ContentNode} is for nodes, that have content in XML documents: text nodes and attributes.
We have three classes: \code{Element} for elements, \code{SimpleData} for text nodes, \code{Attribute} for attributes (see package \code{cz.cuni.mff.ksi.jinfer.base.objects.nodes}).
In theory, the classes and interfaces would be layed out as on fig. \ref{interfaces_nodes}
\begin{figure}
\centering\includegraphics[scale=\myscale]{interfaces_nodes}
\caption{How should interfaces and classes for XML representation look like in theory} \label{interfaces_nodes}
\end{figure}
\begin{figure}
\centering\includegraphics[scale=\myscale]{nodes}
\caption{How are interfaces and classes for XML representation arranged in practice} \label{nodes}
\end{figure}
% This figure has been replaced by UML-like
%\begin{figure}
%\centering\includegraphics[scale=\myscale]{nodes_full}
%\caption{XML representing interfaces and classes in detail} \label{nodes_full}
%\end{figure}
\begin{figure}
\centering\includegraphics[scale=\myscale]{nodes_full2}
\caption{Class diagram for XML representing interfaces and classes} \label{nodes_full2}
\end{figure}

@@

At the present, jInfer modules use the following metadata, all defined in \code{IGGUtils} class:
\begin{itemize}
	\item \code{from.xml}, filled in by \jmodule{BasicIGG} module: means that this rule was created (originates from) from a XML document.
	\item \code{from.schema}, filled in by \jmodule{BasicIGG} and \jmodule{XSDImporter} modules: means that this rule was created (originates from) from a schema.
	\item \code{from.query}, filled in by \jmodule{BasicIGG} and \jmodule{XSDImporter} modules: means that this rule was created from a query.
	\item \code{is.sentinel}, filled in by \jmodule{BasicIGG} and \jmodule{XSDImporter} modules: when importing XML document, one can build whole tree in memory (as in fig. \ref{xml_example}) and then construct list of rules from it (thus saving memory). With schema import however, one not only doesn't know right side of rule in advance (solved by stack in XML import), but right side can be defined anywhere in source file. To save complicated loading of whole schema, searching and pairing elements thorough rules, nodes on right side of rule are created empty - holding only name of node. Fact, that this node has no more information than it's name and position on right side of rule is denominated by labeling the node as sentinel.
	\item \code{required}, filled in by \jmodule{BasicIGG} and \jmodule{XSDImporter} modules: indicates that the attribute is required.
\end{itemize}
All of these metadata are of set/not set character (using \code{Boolean.TRUE} as value, but their presence effectively means "true").
